How to Name a Real-World Object, and how not

### 2019-12-05 papers/ACL2020/acl2020_main.tex

% To streamline frequently used terms:
\newcommand{\mn}{ManyNames\xspace}
\newcommand{\vg}{VisualGenome\xspace}

\title{Something with Objects and Names}

@@

\section{Introduction}
\label{sec:intro}
%\input{introduction}

\begin{itemize}
	\item Real-world objects, being members of many categories, can be called by many names. Nonetheless, humans have a preferred name which they use to call an object (CITE) (\textsl{entry-level name}). 
	\item ...
	\item ...
	\item ...
	\item We adopt an empirical view on the notion of entry-level name, and define it  as the most frequently given name by humans who were asked to name an object depicted in an image. 
	\item ...
	\item ...
	\item This paper:
	\item We address the problem of (entry-level) object naming, and use the \mn dataset that provides many name annotations per object to obtain entry-level names and their alternatives for each object instance. 
	\item Contributions are XXX:
	\item[(1)] We obtain verified name responses for each object in \mn, along with name sets of originally wrongly identified objects. 
	\item We provide an analysis of naming variation: Agreement, number of alternatives, ...
	\item[(2)] ...
\end{itemize}

>>>>

% To streamline frequently used terms:
\newcommand{\langvis}{language\ \&\ vision\xspace}
\newcommand{\lv}{L\&V\xspace}
\newcommand{\mn}{ManyNames\xspace}
\newcommand{\vg}{VisualGenome\xspace}

\newcommand{\cat}[1]{\textsc{#1}}
\newcommand{\name}[1]{\textsl{#1}}

\title{How to Name a Real-World Object, and how not}

@@

\section{Introduction}
\label{sec:intro}
\input{introduction}
